On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-08 Manuscript/manuscript.tex
Comment about Exponential Difference

@@

\subsection*{Exponential Marginal Distribution}
For an exponential marginal distribution, the empirical coverage rates for 
$\mu$, $\sigma_w$, %\eds{define $\sigma_w$} 
%\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} 
and 
the lag-1 autocorrelation coefficient, %\mc{replaced $\phi$ here, as I understand
%it, we are not using $\phi$ in reference to the temporal dependence of the 
%exponentially distributed series?}, 
as well as 95\%
confidence intervals of the real coverage are displayed in 
\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi2}}. 
Additionally, a set of 50 CIs are displayed for each of the percentile, 
BC, and recentered percentile approaches for exponentially distributed
samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
($\phi = 0.4$) in Figure~\ref{fig:eri}.

It appears that a greater sample size is generally required for the bootstrap
CIs to cover the mean and standard deviation parameters in the exponential
margin case than in the normal margin case. However, the trends and patterns
discussed in the main text regarding the performance of various methods and
diverse parameters remain consistent. For example, Student's $t$ confidence
intervals still exhibit higher coverage rates in comparison to alternative
methods. Performance continues to be more favorable when temporal dependence is
negative rather than positive. Of particular significance, the 
percentile, BC,
and BCA confidence intervals still display a decline in coverage accuracy for
the lag-1 autocorrelation coefficient as sample size increases as demonstrated
in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
manifesting the same bias issue. On the other hand, the recentered percentile
confidence interval continues to be effective in estimating the temporal 
dependence %\mc{replaced $\phi$ again here} 
due to the
inherent unbiasedness of the original point estimator. In sum, the findings for
series that are marginally exponentially distributed closely mirror those
attained for series that are marginally normally distributed.

@@

One of the goals of this study was to provide some practical recommendations for 
necessary sample sizes when using block bootstrap to estimate parameters of 
serially dependent data. When using Student's $t$ intervals and $\phi$ is 
unknown, the results of this study suggest that an $n \geq 800$ may be necessary 
for common practice to estimate simpler parameters like $\mu$ or $\sigma_x$. If 
$\phi$ is already known, a lesser $n$ may be adequate to estimate these 
parameters. For lower absolute values of $\phi$, a smaller $n$ is sufficient 
when estimating $\sigma_x$. For negative values of $\phi$, coverage of all 
parameters is higher in general. In fact, Student's $t$ seems to over-cover 
$\mu$ for $\phi = - 0.4$ when using smaller sample sizes, meaning that if $\phi$ 
is known to have a very negative value, another CI may be required. However, in 
real world applications, $\phi$ is more commonly found to be positive, so 
Student's $t$ should still be used if $\phi$ is unknown. Lastly, to estimate 
$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient. Although
we have only used serial dependences as strong as 0.4, we have established the 
trend. When estimating $\mu$, we expect coverage rates to decrease as
$\phi$ approaches 1 - as $\phi$ approaches -1, we may observe increased 
over-coverage. When estimating $\sigma$, we expect a larger sample size to
be necessary as $|\phi|$ gets closer to 1. Lastly, when estimating $\phi$ for
a marginal normal distribution, we 
expect a larger sample size to be necessary as $|\phi|$ approaches 0. However, 
for a marginal exponential distribution, we expect coverage rates of $\phi$ to 
respond
to stronger dependences similarly to coverage rates of $\mu$. Further
investigation may be necessary to see if there are other percentile-based 
interval corrections
that fix the coverage deterioration problem for $\phi$.

>>>>

\subsection*{Exponential Marginal Distribution}
For an exponential marginal distribution, the empirical coverage rates for 
$\mu$, $\sigma_w$, %\eds{define $\sigma_w$} 
%\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} 
and 
the lag-1 autocorrelation coefficient, %\mc{replaced $\phi$ here, as I understand
%it, we are not using $\phi$ in reference to the temporal dependence of the 
%exponentially distributed series?}, 
as well as 95\%
confidence intervals of the real coverage are displayed in 
\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi1}}. 
Additionally, a set of 50 CIs are displayed for each of the percentile, 
BC, and recentered percentile approaches for exponentially distributed
samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
($\phi = 0.4$) in Figure~\ref{fig:eri}.

@@

It appears that a greater sample size is generally required for the bootstrap
CIs to cover the mean and standard deviation parameters in the exponential
margin case than in the normal margin case. In contrast to the marginal normal
distribution, where coverage rates of were greater for stronger dependences 
regardless of the sign, coverage rates seem to be greater only for stronger 
negative
dependencies and lesser for stronger positive dependences. 
\mc{What could be an explanation for this?}
However, the other 
trends 
and patterns
discussed in the main text regarding the performance of various methods and
diverse parameters remain consistent. For example, Student's $t$ confidence
intervals still exhibit higher coverage rates in comparison to alternative
methods. Performance continues to be more favorable when temporal dependence is
negative rather than positive. Of particular significance, the 
percentile, BC,
and BCA confidence intervals still display a decline in coverage accuracy for
the lag-1 autocorrelation coefficient as sample size increases as demonstrated
in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
manifesting the same bias issue. On the other hand, the recentered percentile
confidence interval continues to be effective in estimating the temporal 
dependence 
due to the
inherent unbiasedness of the original point estimator. In sum, 
for the most part, the findings for
series that are marginally exponentially distributed closely mirror those
attained for series that are marginally normally distributed.

@@

One of the goals of this study was to provide some practical recommendations for 
necessary sample sizes when using block bootstrap to estimate parameters of 
serially dependent data. When using Student's $t$ intervals and $\phi$ is 
unknown, the results of this study suggest that an $n \geq 800$ may be necessary 
for common practice to estimate simpler parameters like $\mu$ or $\sigma_x$. If 
$\phi$ is already known, a lesser $n$ may be adequate to estimate these 
parameters. For lower absolute values of $\phi$, a smaller $n$ is sufficient 
when estimating $\sigma_x$. For negative values of $\phi$, coverage of all 
parameters is higher in general. In fact, Student's $t$ seems to over-cover 
$\mu$ for $\phi = - 0.4$ when using smaller sample sizes, meaning that if $\phi$ 
is known to have a very negative value, another CI may be required. However, in 
real world applications, $\phi$ is more commonly found to be positive, so 
Student's $t$ should still be used if $\phi$ is unknown. Lastly, to estimate 
$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient. Further
investigation may be necessary to see if there are other percentile-based 
interval corrections
that fix the coverage deterioration problem for $\phi$.

Although
we have only used serial dependences as strong as 0.4, we have established the 
trends as $|\phi|$ gets larger. When estimating $\mu$, we expect coverage rates 
to decrease as
$\phi$ approaches 1 - as $\phi$ approaches -1, we may observe increased 
over-coverage. When estimating $\sigma$, we expect a larger sample size to
be necessary as $|\phi|$ gets closer to 1. Lastly, when estimating $\phi$ for
a marginal normal distribution, we 
expect a larger sample size to be necessary as $|\phi|$ approaches 0. However, 
for a marginal exponential distribution, we expect coverage rates of the 
first-order autocorrelation to 
respond
to stronger dependences in a trend similar to that of coverage rates of $\mu$.
